### 2008-09-05 trunk/Papers/rmrs-08/entailment.tex
entailment bits

This theorem doesn't provide 
efficient
algorithms for entailment checking, and of course this would be
required to make parser comparison and integration with {\sc rmrs}
practical.  Computing the solved forms of $\varphi$ and $\varphi'$ may
be exponential, and the complexity of the {\sc rmrs} validity problem
is still unknown.  However, the above theorem illustrates that our
model theory for {\sc rmrs} functions in the way it should for parser
comparison and integration, and it can thus be used to prove important
logical properties of shallow parsing systems that adopt {\sc rmrs}.

@@

  ``$\Rightarrow$'': Assume that $\varphi \models \varphi'$, and let
  $s$ be an arbitrary solved form of $\varphi$.  We need to show that
  we can remove atoms from $s$ such that $s$ remains an extension of
  the resulting $s'$ and $s'$ is a solved form of $\varphi'$.

@@

  It is obvious that $s$ is an extension of $s'$.  Furthermore, $s'$
  is in solved form, because $s$ was a tree already and we didn't
  introduce new edges.  The tricky part is to show that $s'$ is a
  solved form of $\varphi'$.  $s'$ contains all labeling atoms of
  $\varphi'$ according to
  Lemma~\ref{lem:entailment-preserves-labeling-atoms}; a similar
  argument holds for inequality atoms.  Finally, $D(\varphi')
  \subseteq D(s')$ because $M,\alpha \models s'$ and $s'$ is
  tree-shaped and normal and therefore contains all statements about
  dominance that are true in $M$.
\end{proof}

>>>>

This theorem doesn't provide 
efficient
algorithms for entailment checking, and this is needed
for parser comparison and integration to be
practical.  Computing the solved forms of $\varphi$ and $\varphi'$ may
be exponential, and the complexity of the {\sc rmrs} validity problem
is unknown.  However, the above theorem illustrates that our
model theory functions in the way it should for parser
comparison and integration, and it can thus be used to prove important
logical properties of shallow parsing systems that adopt {\sc rmrs}.

@@

  ``$\Rightarrow$'': Assume that $\varphi \models \varphi'$, and let
  $s$ be a solved form of $\varphi$.  We need to show that
  we can remove atoms from $s$ such that $s$ remains an extension of
  the resulting $s'$ and $s'$ is a solved form of $\varphi'$.

@@

  It is obvious that $s$ is an extension of $s'$.  Furthermore, $s'$
  is in solved form, because $s$ was a tree and we didn't
  introduce new edges.  The tricky part is to show that $s'$ is a
  solved form of $\varphi'$.  $s'$ contains all labeling atoms of
  $\varphi'$ according to
  Lemma~\ref{lem:entailment-preserves-labeling-atoms}; a similar
  argument holds for inequality atoms.  Finally, $D(\varphi')
  \subseteq D(s')$ because $M,\alpha \models s'$ and $s'$ is
  tree-shaped and normal and therefore contains all dominance statements
  that are true in $M$.
\end{proof}
